Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-17 draft.tex
Added paragraph discussing Fearon 1994

\subsection{Unrecognized States in the Literature}

%Political scientists care a great deal about both civil conflict and about state formation, but unrecognized states do not sit neatly in either literature. The literature on civil war is focused primarily on war onset (e.g. Fearon and Laitin 2003; Hegre and Sambanis 2006), war intensity and duration (e.g. Collier and Hoeffler 2004; Cunningham 2006), and the durability of post-conflict peace (e.g. Hartzell, Hoddie and Rothchild 2001). Unrecognized statehood does not fit neatly into these areas of study because, while unrecognized states begin, and often end, through violent conflict, periods of unrecognized statehood generally contain little, if any, fighting. %Unrecognized statehood often represents a relatively stable end to civil war, but the cessation of fighting is not coterminous with resolution of the conflict in any meaningful way. We argue that persistent unrecognized statehood is not a successful resolution to secessionist civil war; it is a costly and normatively bad outcome in its own right, and it needs to be analyzed as such. 
%Unrecognized states also fall outside most treatments of state formation, because most unrecognized states never achieve recognition (or have not achieved it yet).\footnote{For example, Roeder (2007) treats unrecognized states simply as failures to gain recognized statehood, not as outcomes to be analyzed in their own right.}

@@

>>>>

\subsection{Unrecognized States in the Literature}
%Political scientists care a great deal about both civil conflict and about state formation, but unrecognized states do not sit neatly in either literature. The literature on civil war is focused primarily on war onset (e.g. Fearon and Laitin 2003; Hegre and Sambanis 2006), war intensity and duration (e.g. Collier and Hoeffler 2004; Cunningham 2006), and the durability of post-conflict peace (e.g. Hartzell, Hoddie and Rothchild 2001). Unrecognized statehood does not fit neatly into these areas of study because, while unrecognized states begin, and often end, through violent conflict, periods of unrecognized statehood generally contain little, if any, fighting. %Unrecognized statehood often represents a relatively stable end to civil war, but the cessation of fighting is not coterminous with resolution of the conflict in any meaningful way. We argue that persistent unrecognized statehood is not a successful resolution to secessionist civil war; it is a costly and normatively bad outcome in its own right, and it needs to be analyzed as such. 
%Unrecognized states also fall outside most treatments of state formation, because most unrecognized states never achieve recognition (or have not achieved it yet).\footnote{For example, Roeder (2007) treats unrecognized states simply as failures to gain recognized statehood, not as outcomes to be analyzed in their own right.}

@@

While we do not model this directly, the stability of the status quo equilibrium may be further enhanced by the reluctance of the patron to withdraw support for an unrecognized state that was previously supported. Fearon (1994) and subsequent work on audience costs suggests that, past a certain threshold of escalation, it becomes difficult for leaders to back down from confrontation because they fear looking weak in front of domestic audiences. Leaders of patrons that have supported the secessionists in a previous period may risk losing office if they later back down -- even if it is the best interest of the patron state to do so.
